---
title: "metaPKN"
author: "Aurelien Dugourd"
date: "4/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
library(readr)
library(stringr)
library('org.Hs.eg.db')
library(CARNIVAL) # load CARNIVAL library
library(biomaRt)
library(gsubfn)
library(rpubchem)

setwd("~/Dropbox/COSMOS/")
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
meta_network_carnival_ready_exch_solved <- read_delim("support/meta_network_carnival_ready_exch_solved.tsv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
```

## Preparation of metabolomic inputs

The metabolites in the prior knowledge network are identified as 
XMetab__PUBCHEMID___compartment____, for example "XMetab__1983___r____". The compartment code is the BIGG model standard (r, c, e, x, m, l, n, g). Thus we will first need to map whatever identifer for metabolite the data has to the one of the network.

First, we import the metabolic differential analysis dataframe, the mapping from metabolite name to kegg, the mapping from kegg to pubchem and the PKN.

It is up to the users to find the apprioriate mapping tables to map their identifiers to 
pubchem ones. an example of a uefull ressourcefor that is : 
"http://csbg.cnb.csic.es/mbrole/conversion.jsp"


```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
ttop_tumour_vs_healthy <- as.data.frame(
  read_csv("results/metabolomic/ttop_tumour_vs_healthy.csv"))
metab_to_kegg <- as.data.frame(
  read_csv("support/metab_to_kegg.txt"))
kegg_to_pubchem <- as.data.frame(
  read_csv("support/kegg_to_pubchem.txt", 
           col_names = FALSE))
meta_network_with_X <- as.data.frame(
  read_delim("support/meta_network_carnival_ready_exch_solved.tsv", 
             "\t", escape_double = FALSE, trim_ws = TRUE))

```

Now we will format the pubchem IDs of the kegg to puchem table by adding the apprioriate 
prefixes and suffixes so that they can be mapped on the PKN.

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
kegg_to_pubchem$X2 <- paste("XMetab__",kegg_to_pubchem$X2, sep = "")

compartment_codes <- unique(c(meta_network_with_X$source,meta_network_with_X$target))
compartment_codes <- compartment_codes[grepl("Metab",compartment_codes)]
compartment_codes <- unique(str_match(compartment_codes,"___.____"))

compartment_mapping <- list()
for(i in 1:length(compartment_codes))
{
  df <- kegg_to_pubchem
  df$X2 <- paste(df$X2, compartment_codes[i], sep = "")
  compartment_mapping[[i]] <- df
}

compartment_mapping <- as.data.frame(do.call(rbind, compartment_mapping))

compartment_mapping <- compartment_mapping[
  compartment_mapping$X2 %in% meta_network_with_X$source |
    compartment_mapping$X2 %in% meta_network_with_X$target,
  ]

kegg_to_pubchem_with_comp <- compartment_mapping
names(kegg_to_pubchem_with_comp) <- c("KEGG","pubchem")
```

Now in this instance, we will combine the mapping table to have the connections from original metabolite name used here to the matching identifiers of the PKN. A consequence of this is that a same metabolites can be mapped at multiple places in the PKN.

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
full_mapping <- merge(metab_to_kegg, kegg_to_pubchem_with_comp, by = "KEGG")

names(ttop_tumour_vs_healthy)[1] <- "metab_name"

ttop_tumour_vs_healthy <- merge(ttop_tumour_vs_healthy, full_mapping, by = "metab_name")
ttop_tumour_vs_healthy <- ttop_tumour_vs_healthy[,c(9,2:7)]
```

## Preparation of signaling (kinase/phosphatases and TFs)

Next we need to format the kinases/phosphatases and TF activities into a the proper 
format for CARNIVAL. First we map the gene symbole identifiers to corresponding entrez 
IDs and we add an X at the beginning of each of them so that there are not confused for numbers. Then, we combine both kinases/phospahatases and TFs activities dataframes.

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
##KINASE/PHOSPHATASES
kinase_activities <- as.data.frame(
  read_csv("results/phospho/kinase_activities.csv"))

symbols <- kinase_activities$X1

# use mapIds method to obtain Entrez IDs
mapping_symbole_to_entrez <- mapIds(org.Hs.eg.db, symbols, 'ENTREZID', 'SYMBOL')
for(i in 1:length(kinase_activities[,1]))
{
  kinase_activities[i,1] <- mapping_symbole_to_entrez[kinase_activities[i,1]]
}

kinase_activities <- kinase_activities[complete.cases(kinase_activities),]
kinase_activities$X1 <- paste("X", kinase_activities$X1, sep = "")

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
##TF
TF_scores <- as.data.frame(
  read_csv("results/transcriptomic/TF_scores.csv"))

symbols <- TF_scores$ID

# use mapIds method to obtain Entrez IDs
mapping_symbole_to_entrez <- mapIds(org.Hs.eg.db, symbols, 'ENTREZID', 'SYMBOL')
for(i in 1:length(TF_scores[,1]))
{
  TF_scores[i,1] <- mapping_symbole_to_entrez[TF_scores[i,1]]
}

TF_scores <- TF_scores[complete.cases(TF_scores),]
TF_scores$ID <- paste("X", TF_scores$ID, sep = "")

##Combine TF and kinase
names(TF_scores) <- c("X1","NES")
kinase_activities <- as.data.frame(rbind(kinase_activities, TF_scores))
```

Now we need to convert the dataframe of activities and metabolomic abundance changes into
as single row dataframe with column names as genes and metabolite 
identifiers. We also keep only significant activities and abundance changes as input 
(threshold at users discretion, here we use 0.05 p-value for metabolites and abs(NES) > 
1.7 for TFs, kinases and phosphatases). We also convert the continuous values into 1 and -1.

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
#### Input formatting

metab_input_carnival <- ttop_tumour_vs_healthy[ttop_tumour_vs_healthy$P.Value < 0.05,c(1,4)]
metab_input_carnival <- metab_input_carnival[metab_input_carnival$pubchem %in% meta_network_with_X$source | metab_input_carnival$pubchem %in% meta_network_with_X$target,]
metabs <- metab_input_carnival$pubchem
metab_input_carnival <- as.data.frame(sign(t(metab_input_carnival[,2])))
names(metab_input_carnival) <- metabs

signaling_input_carnival <- kinase_activities[abs(kinase_activities$NES) > 1.7,]
signaling_input_carnival <- signaling_input_carnival[signaling_input_carnival$X1 %in% meta_network_with_X$source | signaling_input_carnival$X1 %in% meta_network_with_X$target,]
signaling_enzymes <- signaling_input_carnival$X1
signaling_input_carnival <- as.data.frame(sign(t(signaling_input_carnival[,2])))
names(signaling_input_carnival) <- signaling_enzymes

write_csv(metab_input_carnival, "results/metabolomic/metab_input_carnival.csv")
write_tsv(metab_input_carnival, "results/metabolomic/metab_input_carnival.tsv")

write_csv(signaling_input_carnival, "results/phospho/signaling_input_carnival.csv")
write_tsv(signaling_input_carnival, "results/phospho/signaling_input_carnival.tsv")
```

Finally, we do some cleaning on the PKN, removing characters that are not compatible with carnival as well as dupplicated intercations.

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
meta_network_with_X$source <- gsub("[-+{},;() ]","______",meta_network_with_X$source)
meta_network_with_X$target <- gsub("[-+{},;() ]","______",meta_network_with_X$target)

isdup <- rep(FALSE,length(meta_network_with_X[,1]))
for(i in 1:length(meta_network_with_X[,1]))
{
  isdup[i] <- meta_network_with_X[i,1] == meta_network_with_X[i,3]
}
meta_network_with_X <- meta_network_with_X[!isdup,]
meta_network_with_X <- unique(meta_network_with_X)

write_tsv(meta_network_with_X, "support/meta_network_with_X_nobadchar.tsv")
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
# CARNIVAL_Result <- runCARNIVAL(CplexPath="~/Documents/cplex",
#                                Result_dir="results/multi_omic/carnival/",
#                                CARNIVAL_example=NULL,
#                                UP2GS=F,
#                                netFile = "support/meta_network_with_X_nobadchar.tsv", 
#                                measFile = "results/metabolomic/metab_input_carnival.tsv", 
#                                inputFile = "results/phospho/signaling_input_carnival.tsv",
#                                weightFile = NULL, 
#                                timelimit = 7200,
#                                mipGAP = 0.12
#                                
# ) #11.24
# 
# CARNIVAL_Result2 <- runCARNIVAL(CplexPath="~/Documents/cplex",
#                                 Result_dir="results/multi_omic/carnival/",
#                                 CARNIVAL_example=NULL,
#                                 UP2GS=F,
#                                 netFile = "support/meta_network_with_X_nobadchar.tsv", 
#                                 measFile = "results/phospho/signaling_input_carnival.tsv", 
#                                 inputFile = "results/metabolomic/metab_input_carnival.tsv",
#                                 weightFile = NULL, 
#                                 timelimit = 7200
# )# 2.44
# 
# save(CARNIVAL_Result,file = "results/multi_omic/CARNIVAL_result_forward.RData")
# save(CARNIVAL_Result2,file = "results/multi_omic/CARNIVAL_result_backward.RData")
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
load("results/multi_omic/CARNIVAL_result_forward.RData")
load("results/multi_omic/CARNIVAL_result_backward.RData")
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
signaling_input_carnival <- as.data.frame(
  read_delim("results/phospho/signaling_input_carnival.tsv",
             "\t", escape_double = FALSE, trim_ws = TRUE))

metab_input_carnival <- as.data.frame(
  read_delim("results/metabolomic/metab_input_carnival.tsv",
             "\t", escape_double = FALSE, trim_ws = TRUE))

sif <- as.data.frame(CARNIVAL_Result[[1]]$weightedSIF)
sif2 <- as.data.frame(CARNIVAL_Result2[[1]]$weightedSIF)

sif$Node1 <- gsub("^X","",sif$Node1)
sif$Node2 <- gsub("^X","",sif$Node2)

sif2$Node1 <- gsub("^X","",sif2$Node1)
sif2$Node2 <- gsub("^X","",sif2$Node2)

att <- as.data.frame(CARNIVAL_Result[[1]]$attributesAll)#[,c(1,2)]
att$measured <- ifelse(att$Nodes %in% names(signaling_input_carnival) | att$Nodes %in% names(metab_input_carnival), 1, 0)
att$Nodes <- gsub("^X","",att$Nodes)

att2 <- as.data.frame(CARNIVAL_Result2[[1]]$attributesAll)#[,c(1,2)]
att2$measured <- ifelse(att2$Nodes %in% names(signaling_input_carnival) | att2$Nodes %in% names(metab_input_carnival), 1, 0)
att2$Nodes <- gsub("^X","",att2$Nodes)

att$type <- ifelse(grepl("Metab",att$Nodes), "metabolite","protein")
att2$type <- ifelse(grepl("Metab",att2$Nodes), "metabolite","protein")


########################
prots <- unique(c(att$Nodes, att2$Nodes))
prots <- prots[!(grepl("Metab",prots))]
prots <- gsub("Gene[0-9]+__","",prots)
prots <- gsub("_reverse","",prots)
prots <- gsub("EXCHANGE.*","",prots)
prots <- unique(prots)
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
ensembl = useEnsembl(biomart="ensembl", dataset="hsapiens_gene_ensembl")

G_list <- getBM(filters = "entrezgene_id",
                attributes = c('hgnc_symbol','entrezgene_id', "description"),
                values = prots, mart = ensembl)

gene_mapping <- G_list[,1]
names(gene_mapping) <- G_list[,2]
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}
sif$Node1 <- gsub("_reverse","",sif$Node1)
sif$Node2 <- gsub("_reverse","",sif$Node2)
sif2$Node1 <- gsub("_reverse","",sif2$Node1)
sif2$Node2 <- gsub("_reverse","",sif2$Node2)
att$Nodes <- gsub("_reverse","",att$Nodes)
att2$Nodes <- gsub("_reverse","",att2$Nodes)

sif$Node1 <- gsub("EXCHANGE.*","",sif$Node1)
sif$Node2 <- gsub("EXCHANGE.*","",sif$Node2)
sif2$Node1 <- gsub("EXCHANGE.*","",sif2$Node1)
sif2$Node2 <- gsub("EXCHANGE.*","",sif2$Node2)
att$Nodes <- gsub("EXCHANGE.*","",att$Nodes)
att2$Nodes <- gsub("EXCHANGE.*","",att2$Nodes)

metabs <- unique(c(att$Nodes, att2$Nodes))
metabs <- metabs[(grepl("Metab",metabs))]

metab_to_pubchem <- as.data.frame(read_csv("support/metab_to_pubchem.csv"))
metab_to_pubchem_vec <- metab_to_pubchem$name
names(metab_to_pubchem_vec) <- metab_to_pubchem$pubchem

for(i in 1:length(sif$Node1))
{
  if(gsub("Gene[0-9]+__","",sif[i,1]) %in% names(gene_mapping))
  {
    if(grepl("Gene",sif[i,1]))
    {
      prefix <- gsub("__.*","",sif[i,1])
      sif[i,1] <- paste(prefix,gene_mapping[gsub("Gene[0-9]+__","",sif[i,1])], sep = "__")
    }
    else
    {
      sif[i,1] <- gene_mapping[gsub("Gene[0-9]+__","",sif[i,1])]
    }
  }
  if(gsub("Gene[0-9]+__","",sif[i,3]) %in% names(gene_mapping))
  {
    if(grepl("Gene",sif[i,3]))
    {
      prefix <- gsub("__.*","",sif[i,3])
      sif[i,3] <- paste(prefix,gene_mapping[gsub("Gene[0-9]+__","",sif[i,3])], sep = "__")
    }
    else
    {
      sif[i,3] <- gene_mapping[gsub("Gene[0-9]+__","",sif[i,3])]
    }
  }
  if(gsub("Metab__","",gsub("___[a-z]____","",sif[i,1])) %in% names(metab_to_pubchem_vec))
  {
    suffix <- str_match(sif[i,1],"___.____")
    metab <- metab_to_pubchem_vec[gsub("Metab__","",gsub("___[a-z]____","",sif[i,1]))]
    sif[i,1] <- paste(metab,suffix,sep = "")
  }
  if(gsub("Metab__","",gsub("___[a-z]____","",sif[i,3])) %in% names(metab_to_pubchem_vec))
  {
    suffix <- str_match(sif[i,3],"___.____")
    metab <- metab_to_pubchem_vec[gsub("Metab__","",gsub("___[a-z]____","",sif[i,3]))]
    sif[i,3] <- paste(metab,suffix,sep = "")
  }
}

for(i in 1:length(sif2$Node1))
{
  if(gsub("Gene[0-9]+__","",sif2[i,1]) %in% names(gene_mapping))
  {
    if(grepl("Gene",sif2[i,1]))
    {
      prefix <- gsub("__.*","",sif2[i,1])
      sif2[i,1] <- paste(prefix,gene_mapping[gsub("Gene[0-9]+__","",sif2[i,1])], sep = "__")
    }
    else
    {
      sif2[i,1] <- gene_mapping[gsub("Gene[0-9]+__","",sif2[i,1])]
    }
  }
  if(gsub("Gene[0-9]+__","",sif2[i,3]) %in% names(gene_mapping))
  {
    if(grepl("Gene",sif2[i,3]))
    {
      prefix <- gsub("__.*","",sif2[i,3])
      sif2[i,3] <- paste(prefix,gene_mapping[gsub("Gene[0-9]+__","",sif2[i,3])], sep = "__")
    }
    else
    {
      sif2[i,3] <- gene_mapping[gsub("Gene[0-9]+__","",sif2[i,3])]
    }
  }
  if(gsub("Metab__","",gsub("___[a-z]____","",sif2[i,1])) %in% names(metab_to_pubchem_vec))
  {
    suffix <- str_match(sif2[i,1],"___.____")
    metab <- metab_to_pubchem_vec[gsub("Metab__","",gsub("___[a-z]____","",sif2[i,1]))]
    sif2[i,1] <- paste(metab,suffix,sep = "")
  }
  if(gsub("Metab__","",gsub("___[a-z]____","",sif2[i,3])) %in% names(metab_to_pubchem_vec))
  {
    suffix <- str_match(sif2[i,3],"___.____")
    metab <- metab_to_pubchem_vec[gsub("Metab__","",gsub("___[a-z]____","",sif2[i,3]))]
    sif2[i,3] <- paste(metab,suffix,sep = "")
  }
}

for(i in 1:length(att$Nodes))
{
  if(gsub("Gene[0-9]+__","",att[i,1]) %in% names(gene_mapping))
  {
    if(grepl("Gene",att[i,1]))
    {
      prefix <- gsub("__.*","",att[i,1])
      att[i,1] <- paste(prefix,gene_mapping[gsub("Gene[0-9]+__","",att[i,1])], sep = "__")
    }
    else
    {
      att[i,1] <- gene_mapping[gsub("Gene[0-9]+__","",att[i,1])]
    }
  }
  if(gsub("Metab__","",gsub("___[a-z]____","",att[i,1])) %in% names(metab_to_pubchem_vec))
  {
    suffix <- str_match(att[i,1],"___.____")
    metab <- metab_to_pubchem_vec[gsub("Metab__","",gsub("___[a-z]____","",att[i,1]))]
    att[i,1] <- paste(metab,suffix,sep = "")
  }
}

for(i in 1:length(att2$Nodes))
{
  if(gsub("Gene[0-9]+__","",att2[i,1]) %in% names(gene_mapping))
  {
    if(grepl("Gene",att2[i,1]))
    {
      prefix <- gsub("__.*","",att2[i,1])
      att2[i,1] <- paste(prefix,gene_mapping[gsub("Gene[0-9]+__","",att2[i,1])], sep = "__")
    }
    else
    {
      att2[i,1] <- gene_mapping[gsub("Gene[0-9]+__","",att2[i,1])]
    }
  }
  if(gsub("Metab__","",gsub("___[a-z]____","",att2[i,1])) %in% names(metab_to_pubchem_vec))
  {
    suffix <- str_match(att2[i,1],"___.____")
    metab <- metab_to_pubchem_vec[gsub("Metab__","",gsub("___[a-z]____","",att2[i,1]))]
    att2[i,1] <- paste(metab,suffix,sep = "")
  }
}

########################
url <- paste0(
  'http://omnipathdb.org/ptms?',
  'fields=sources,references&genesymbols=1'
)

download_omnipath <- function(){
  
  read.table(url, sep = '\t', header = TRUE)
  
}

omnipath_ptm <- download_omnipath()
omnipath_ptm <- omnipath_ptm[omnipath_ptm$modification %in% c("dephosphorylation","phosphorylation"),]
KSN <- omnipath_ptm[,c(4,3)]
KSN$substrate_genesymbol <- paste(KSN$substrate_genesymbol,omnipath_ptm$residue_type, sep ="_")
KSN$substrate_genesymbol <- paste(KSN$substrate_genesymbol,omnipath_ptm$residue_offset, sep = "")
KSN$sign <- ifelse(omnipath_ptm$modification == "phosphorylation", 1, -1)

att$type <- ifelse(att$Nodes %in% KSN$enzyme_genesymbol, "Kinase",att$type)

url <- paste0(
  'http://omnipathdb.org/interactions?',
  'datasets=tfregulons&tfregulons_levels=A,B,C&genesymbols=1&fields=sources,tfregulons_level'
)

dorothea <- download_omnipath()
dorothea <- dorothea[,c(4,3,6,7)]
dorothea$sign <- dorothea$is_stimulation - dorothea$is_inhibition
dorothea$sign <- ifelse(dorothea$sign == 0, 1, dorothea$sign)
dorothea <- dorothea[,c(1,2,5)]

att$type <- ifelse(att$Nodes %in% dorothea$source_genesymbol, "TF",att$type)

i <- 1
for(node in att$Nodes) #check if a node name is basename appears more than once in nodes. If so, it is a metabolic enzyme
{
  if(sum(gsub("Gene.*_","",node) == gsub("Gene.*_","",att$Nodes)) > 1)
  {
    att[i,4] <- "metab_enzyme"
  }
  i <- i+1
}

att$type <- ifelse(grepl("Gene.*_",att$Nodes), "metab_enzyme",att$type)

att2$type <- ifelse(att2$Nodes %in% KSN$enzyme_genesymbol, "Kinase",att2$type)

att2$type <- ifelse(att2$Nodes %in% dorothea$source_genesymbol, "TF",att2$type)

i <- 1
for(node in att2$Nodes) #check if a node name is basename appears more than once in nodes. If so, it is a metabolic enzyme
{
  if(sum(gsub("Gene.*_","",node) == gsub("Gene.*_","",att2$Nodes)) > 1)
  {
    att2[i,4] <- "metab_enzyme"
  }
  i <- i+1
}

att2$type <- ifelse(grepl("Gene.*_",att2$Nodes), "metab_enzyme",att2$type)

att$Activity <- sign(as.numeric(as.character(att$Activity)))
att2$Activity <- sign(as.numeric(as.character(att2$Activity)))

sif$Node1 <- gsub("Gene[0-9]+__","",sif$Node1)
sif$Node2 <- gsub("Gene[0-9]+__","",sif$Node2)
att$Nodes <- gsub("Gene[0-9]+__","",att$Nodes)

sif2$Node1 <- gsub("Gene[0-9]+__","",sif2$Node1)
sif2$Node2 <- gsub("Gene[0-9]+__","",sif2$Node2)
att2$Nodes <- gsub("Gene[0-9]+__","",att2$Nodes)

sif <- sif[sif$Node1 != sif$Node2,]
sif2 <- sif2[sif2$Node1 != sif2$Node2,]

sif$Node1 <- gsub("[_]{3,5}","_",sif$Node1)
sif$Node2 <- gsub("[_]{3,5}","_",sif$Node2)
att$Nodes <- gsub("[_]{3,5}","_",att$Nodes)

sif2$Node1 <- gsub("[_]{3,5}","_",sif2$Node1)
sif2$Node2 <- gsub("[_]{3,5}","_",sif2$Node2)
att2$Nodes <- gsub("[_]{3,5}","_",att2$Nodes)

sif3 <- as.data.frame(rbind(sif[as.numeric(as.character(sif$Weight)) >= 80,], sif2[as.numeric(as.character(sif2$Weight)) >= 80,]))
```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```

```{r, message=FALSE, warning=FALSE,results='hide',fig.keep='all', fig.height=4, fig.width=12}

```